MoneyBallR_RMD

### 2019-09-20 hw1/results/MoneyBallR_RMD.Rmd
Add files via upload

#Principal Components
```{r}
#PCA Analysis in R DataCamp Article
library(tidyverse)

mtcars.pca <- prcomp(mtcars[,c(1:7,10,11)], center = TRUE,scale. = TRUE) #exclude the categorical variables

mtcars <- mtcars

summary(mtcars.pca)

str(mtcars.pca)

ggbiplot(mtcars.pca) # this shows you what attributes contribute to principal component 1 and 2

ggbiplot(mtcars.pca, labels=rownames(mtcars)) # add in the sample information

mtcars.country <- c(rep("Japan", 3), rep("US",4), rep("Europe", 7),rep("US",3), "Europe", rep("Japan", 3), rep("US",4), rep("Europe", 3), "US", rep("Europe", 3))

ggbiplot(mtcars.pca,ellipse=TRUE,  labels=rownames(mtcars), groups=mtcars.country) #represent circles around groupings I want to do this binary classifiers

>>>>

#Principal Components
```{r}
